Summary Tables ITHIMR

### 2019-05-03 summary_tables_PA_AP.Rmd
changed summary PA_AP - distance and source apportionment

@@

select<- c("car", "motorcycle", "walking", "bicycle", "bus")
io[[cities[x]]]$trip_scen_sets <-io[[cities[x]]]$trip_scen_sets[io[[cities[x]]]$trip_scen_sets$trip_mode %in% select,]

dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance))
dist_scen<- as.data.frame (dist_scen)
names(dist_scen)[3]<-"distance"
dist_scen<-spread(dist_scen, trip_mode, distance)

dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen)-1)], na.rm = FALSE, dims = 1)
dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen)-1)]*100/dist_scen$sum, digits=1)
dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop)

>>>>

# Descriptive tables of emission inventory

city<-cities
trans_share<-c(22.5, 40.0, 22.5, 28.1) 
pm_conc<- c(50, 18, 122, 47 )
shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc))
names(shares)[2]<- "trans_share"
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- "emissions"
  summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1)
  print (as.character(cities[x]))
  summary(as.data.frame(summary))
  summary[nrow(summary)+1,1]<-"Transport share"
  summary[nrow(summary),2]<-as.character(shares$trans_share[x])
  summary[nrow(summary)+1,1]<-"PM2.5 Conc"
  summary[nrow(summary),2]<-as.character(shares$pm_conc[x])
  print (summary)

}

@@

  select<- c("car", "motorcycle", "walking", "bicycle", "bus")

  io[[cities[x]]]$trip_scen_sets$trip_mode[!io[[cities[x]]]$trip_scen_sets$trip_mode %in% select]<- "other"

  dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance))
  dist_scen<- as.data.frame (dist_scen)
  names(dist_scen)[3]<-"distance"
  dist_scen$distance<- round(dist_scen$distance, digits=0)
    dist_scen<-spread(dist_scen, trip_mode, distance)
  dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen))], na.rm = FALSE, dims = 1)
  dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen))]*100/dist_scen$sum, digits=1)
  dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop)
